Moral Foundations of U.S. Political News Organizations

### 2019-02-02 pilot_manuscript.Rmd
finally fixed Congressional Record citation

In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice. Kavanaugh was previously on the U.S. Court of Appeals for the District of Columbia. The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 [@CITE_CONGRESSIONAL_RECORD]. Following allegations of sexual assault by high school classmate Dr. Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.

On September 27, the committee questioned Dr. Ford before commencing a second round of questioning for Judge Kavanaugh [@CITE_CONGRESSIONAL_RECORD]. During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh. According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television [@OConnell2018]. This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States. On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor. Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved. The investigation concluded with no significant findings. The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@CITE_CONGRESSIONAL_RECORD].

>>>>

In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice. Kavanaugh was previously on the U.S. Court of Appeals for the District of Columbia. The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 [@USGovernment2018b]. Following allegations of sexual assault by high school classmate Dr. Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.

On September 27, the committee questioned Dr. Ford before commencing a second round of questioning for Judge Kavanaugh [@USGovernment2018]. During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh. According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television [@OConnell2018]. This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States. On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor. Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved. The investigation concluded with no significant findings. The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@USGovernment2018a].
